% internship.tex
\documentclass{beamer}
\usetheme[hideothersubsections,height=6mm]{Berkeley}
\setbeamertemplate{navigation symbols}{}

\usepackage{color}
\usepackage[ascii]{inputenc}
\usepackage{hyperref}


\title{ECSIG Resources}
\subtitle{What we use every day.}
\author{Greg Gardner}
\date{17 September 2013}

\begin{document}

\frame{\titlepage}

%\begin{frame}{Outline}
%  \tableofcontents
%\end{frame}

\section{Who}
\begin{frame}{Who We Are}
We are a group of Computer Science students with a passion for technology. \\\hfill
	
We come together to exchange ideas and learn more about the tools and concepts that make Computer Science fun.\\\hfill

  \begin{block}{Comp.Sci. is boring bro, why even bother?}
	False!  Comp. Sci. is awesome and constantly changing.  If you dislike using a tool or rewriting the same old code, chances are someone else has been there and written something better.  Exploring new solutions is what our proffession is all about!
  \end{block}
\end{frame}

\section{What}
\begin{frame}\frametitle{What We Are}
We are URI's ACM student chapter.\\\hfill

E.C.S.I.G stands for:
  \begin{itemize}
    \item {\bf E}ngineering
    \item {\bf C}omputer
		\item {\bf S}cience
		\item {\bf I}nterest
		\item {\bf G}roup
  \end{itemize}

\end{frame}

\section{Resources}
\begin{frame}\frametitle{Resources: Communication}

	\begin{itemize}
		\item {\bf IRC} -- irc.ecsig.com\\
Our main channel of communication, where we casually talk about programming, course material, lolcatz, etc.
		\item {\bf Forums} -- forums.ecsig.com \\
Discussions about projects, presentations, and workshops.
		\item {\bf Weekly Meetings}\\
Tuesdays at 5:30pm in Tyler 055.
		\item {\bf Google Hangouts}\\
Hangouts are used for members that cannot attend meetings in person, as well as for organising impromtu disscussions.\\
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Resources: Projects}
ECSIG is a community for learning and discovery. We are active in many ways.

	\begin{itemize} 
		\item {\bf Presentations}\\
Members often volunteer to present cool stuff at meetings.
		\item {\bf Workshops}\\
Events for teaching non-members critical software engineering skills. Roughly once or twice a semester.
		\item {\bf Side Projects}\\
Members are encouraged to do their own projects and present them.
	\end{itemize}

	\end{frame}
\end{document}
